### 2020-04-15 survival.tex
readded sections with modified pdfs
Cleaning up.
km plots into one

\section{Survival Analysis}
\label{sec:survival}
 Kaplan-Meier survival analysis (KM) gives the probability of survival
beyond a given time. It is a nonparametric technique that makes no
specific failure model assumptions, such as Weibull, Exponential,
etc. It can also split the data into subpopulations and compute
separate survival curves.

@@

We use reliability censoring concepts to use information from units
that were proactively removed before failing as well as those still in
operation till the end. We use the R package {\tt survival} for the KM
analysis.
\begin{figure}
  \centering
  \includegraphics[width=6in]{figs/km_cage-node_o001.pdf}
  \caption{Survival probability from Kaplan-Meier analysis for {\tt
      old} batch GPUs, stratified by {\tt cage} and {\tt node}.}
  \label{fig:km-old-cage-node}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=6in]{figs/km_cage-node_c001.pdf}
  \caption{Comparison of the old and new batches, focusing only on
    three years of operation of the new batch so far.}
  \label{fig:km-all-cage-node}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=5in]{figs/cox_o001.pdf}
  \caption{GPU hazard ratios from Cox regression model on {\tt old}
    batch.}
\end{figure}
\begin{figure}
  \includegraphics[width=5in]{figs/cox_n001.pdf}
  \caption{GPU hazard ratios from Cox regression model on {\tt new}
    batch.}
\end{figure}

>>>>

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Survival Analysis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survival Analysis}
\label{section:survival}

 Kaplan-Meier survival analysis (KM) gives the probability of survival
beyond a given time. It is a nonparametric technique that makes no
specific failure model assumptions, such as Weibull, Exponential,
etc. It can also split the data into subpopulations and compute
separate survival curves.

@@

We use reliability censoring concepts to use information from units
that were proactively removed before failing as well as those still in
operation till the end. We use the R package {\tt survival} for the KM
analysis.
\begin{figure*}
  \centering
  \includegraphics[width=7in]{figs/km_cage-node_a001.pdf}
  \caption{Comparison of the old and new batches, including survival
    differences based on {\tt cage} and {\tt node} GPU locations.}
  \label{fig:km-all-cage-node}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=6.5in]{figs/cox_o001.pdf}
  \caption{GPU hazard ratios from Cox regression model on {\tt old}
    batch.}
\end{figure*}
\begin{figure*}
  \includegraphics[width=6.5in]{figs/cox_n001.pdf}
  \caption{GPU hazard ratios from Cox regression model on {\tt new}
    batch.}
\end{figure*}
